\documentclass[10pt,a4paper]{article}
% usepackages
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
% math
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{latexsym}
% formatting
\usepackage{parskip}
\usepackage{fullpage}
\usepackage{pgf,tikz}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\pagestyle{empty}
% graphics
%\usepackage[pdftex]{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage[below,section]{placeins} % the one below is better for short assignments
\usepackage{float} % provides H as float placement specifier
% extras
\usepackage[pdftex,a4paper,colorlinks=true,urlcolor=blue]{hyperref}
\urlstyle{same}
\usepackage{moreverb} %\verbatimtabinput{filename.py} preserves indentation

%Numbering first level list roman (i,ii,iii) instead of arabic (1,2,3)
% options are \roman \Roman \alph \Alph \arabic
\renewcommand{\theenumi}{\roman{enumi}} 
\renewcommand{\theenumii}{\roman{enumii}}
\newcommand{\Int}{\int\limits}
% Also achieved with the enumerate package
\usepackage{enumerate}
%\numberwithin{equation}{section}%

% author/title details
\author{Alice NANYANZI (\href{mailto:alicenanyanzi@aims.ac.za}{alicenanyanzi@aims.ac.za})}
% \title{Course Title: Assignment X}
\title{Report: 16th-27th January, 2017}
\begin{document}
\maketitle
\section*{Week 1 (16th-20th January,2017):}
Revision of my Structured Masters Essay (Laplacian Matrix of a Network and Applications). Focus was mainly on the centrality measures and Laplacian matrix.\\\\
Revision Guiding Questions included?
\begin{itemize}
\item What is meant by centrality of anode?
\item Why is it important to compute the centrality of a node with in the network?
\item Explain the different centrality measures and their applications in the real-world.
\item Any correlation between the different centrality measure? Explanation for results?
\item Do you think there exists new determinants of importance of a node that are not addressed within the existing centrality measures?
\item Why is it called the Laplacian?
\item What is the importance of the Laplacian?
\item Explain some of the applications of the Laplacian.
\item Can you think of some other applications of the Laplacian?
\item How about Laplacian matrix of a directed network? What are its properties? Any applications in real world?
\end{itemize}
\section*{Week 2 (23rd-27th January,2017):}
\begin{enumerate}[a)]
\item Ford-Furkerson Algorithm (FFA) for flow networks:
\begin{itemize}
\item What are flow networks?
\item Examples of such networks in real-world
\item operation of the Ford-Furkerson Algorithm for maximum flow
\item What is maximum cut in FFA?
\item Can we use the Laplacian matrix to compute the maximum cut in a flow network? 
\end{itemize}
\item Consensus in Networks:
\begin{itemize}
\item What is consensus?
\item Examples of real world scenarios where consensus is applied?
\item Application of Laplacian matrices in the analysis of consensus in networks
\item Long range interactions- may be grouped under physical or social influences. \\\\
Regarding the social influence, using the analogy of finance theory, why is the Future value of information always greater than the present value.
\item Can we think of any other kind of influence or method for modelling long range interactions?
\end{itemize}
\end{enumerate}

\end{document}
